Soybean herbicide study - Dan Smith

### 2020-10-28 soyherb.Rmd
as

---
title: "Soybean herbicide study - Dan Smith"
author: "Maxwel Coura Oliveira"
date: "10/28/2020"
output: 
  html_document: 
    toc: yes
    highlight: zenburn
    theme: simplex
    number_sections: yes
---

@@

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(kableExtra)
```

@@

@@

#### Herbicide

```{r }
lsmeans_28<- emmeans(model_28_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
```

@@

>>>>

---
title: "Soybean herbicide study - Dan Smith"
author: "Maxwel Coura Oliveira"
date: "10/28/2020"
output: 
  html_document: 
    toc: yes
    theme: yeti
    number_sections: yes
    toc_depth: 4
    highlight: espresso
---

@@

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(kableExtra)
library(lme4)
library(lmerTest)
```

@@

## Weed biomass

```{r fig.align='center', message=FALSE, warning=FALSE}
ggplot(data, aes(x=reorder(other,biomass_gm2), y=biomass_gm2,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Weed biomass (g m2)") +
  theme_minimal() +
  theme(legend.position = "none")
```

@@

```{r }
lsmeans_28 <- emmeans(model_28_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
```

@@

## Yield

### Yield raw data distribution

```{r warning=FALSE, message=FALSE}
library(ggridges)
new_dt %>% 
  ggplot(
    aes(y=herbicide, x=yield_kg, fill=herbicide)) +
      geom_density_ridges(scale=2, show.legend = FALSE)
```

### Data manipulation

```{r warning=FALSE, message=FALSE}
yield_dt <- new_dt %>% 
  mutate(
    siteyr = case_when(
      location == "Lancaster" & year == 2020 ~ "Lan20",
      location == "Lancaster" & year == 2019 ~ "Lan19",
      location == "Brooklyn" & year == 2020 ~ "Bro20",
      location == "Brooklyn" & year == 2019 ~ "Bro19",
      TRUE                     ~  "siteyr"
    )
  )
```

```{r warning=FALSE}
fit <- lmer(yield_kg ~ herbicide * siteyr + (1|rep), data=yield_dt)
```

```{r}
anova(fit)
```

```{r }
lsmeans_fit <- emmeans(fit, ~ siteyr, cont="pairwise", adjust="none", alpha=0.05)
```

```{r fig.align='center'}
plot(lsmeans_fit, ~ siteyr, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
```

```{r message=FALSE, warning =FALSE}
CLD(lsmeans_fit$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

<br><br>

```{r echo=FALSE, out.width=400, fig.align='center'}
knitr::include_graphics("https://media.giphy.com/media/l0Iyl55kTeh71nTXy/giphy.gif")
```
